Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

\documentclass[AMS,STIX1COL]{WileyNJD-v2}
%\documentclass[AMS]{WileyNJD-v2}
\usepackage{graphicx,times,verbatim,amsmath,amsthm}
%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{float}  % For fixing the image in draft
\usepackage{lscape}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\newcommand{\block}[1]{
  \underbrace{\begin{matrix}1 & \cdots & 1\end{matrix}}_{#1}
}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{condition}[theorem]{Condition}
%\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{property}[theorem]{Property}
%\newtheorem{result}[theorem]{Result}
%\newtheorem{example}[theorem]{Example}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

@@

\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, ADMM}

\jnlcitation{\cname{%
\author{Suh Namjoon.},
\author{Xiaoming Huo},
\author{Eric Heim},
\author{Timothy Van Slyke}, and
\author{Lee Seversky}} (\cyear{2019}),
\ctitle{Citation network}, \cjournal{journal.}, \cvol{2019;00:1--6}.}
\maketitle
\footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, ADMM, network model}

@@

\begin{equation}
\label{eq:logistic01}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha + f_i^T D f_j }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$.
We assume $d_{ii} > 0$ for $1 \le i \le K$.
Another way to put \eqref{eq:logistic01} is
\begin{equation}
\label{eq:logistic02}
\mathbb{P}(X_{ij}=1) = \frac{\exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}{1 + \exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}.
\end{equation}
A justification of the above model is that when both node $i$ and node $j$ are related to topic $k$, they have a higher chance to cite one way or the other.
We have assumed a common strengthen coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes.
We denote a matrix $F = \{f_1, f_2, \ldots, f_n\} \in \mathbb{R}^{K \times n}$.
Each column $i$ in matrix $F$ contains the factor loadings associated with the node $i$ ($1\le i \le n$).
Given the diagonal matrix $D$ and the factor loading matrix $F$, we assume that $X_{ij}$'s are independent; therefore we have the total conditional probability function as follows:
\begin{equation}
\label{eq:logistic03}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \prod_{1\le i<j \le n} \mathbb{P}(X_{ij})
= \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha + f_i^T D f_j) }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\mathbb{P}(X_{ij})$ is given in \eqref{eq:logistic02}.
The last equation holds because $X_{ij}$ only takes binary (i.e., $0$ or $1$) values.
Recall that the dot product of two matrices with same dimensionality, $A,B\in \mathbb{R}^{a \times b}$, is defined as $A\bullet B=\mbox{trace}(A^T B) = \sum_{i=1}^a\sum_{j=1}^b a_{ij}b_{ij}$.
The above \eqref{eq:logistic03} can be further rewritten as
\begin{equation}
\label{eq:logistic04}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F)\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where we assume $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
The above delivers a factor analysis model.
Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g.,\cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).

@@

Though it may seem similar to Chen et al \cite{chen2016fused}, we work on a different model formulation in several aspects.
We summarize the differences as follows.
\begin{enumerate}
\item FLaG is built to analyze the Eysenck's Personality Questionnaire that consists of items designed to measure Psychoticism, Extraversion, and Neuroticism.
    So there are $p$ questions that need to be answered, and each questions fall into above three categories.
    If there are $n$ respondents to questions, we have $n$ independent data generated from same distribution.
    In our case, the observed citation network can be thought of as one realization of a random graph.

@@

\item FLaG approximates the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes.
    In our model, likelihood function is directly accessible due to the conditional independence among edges given parameters.
\end{enumerate}

@@

The rest of the paper is organized as follows.
In Section \ref{sec:model-form}, we will give a presentation on how to build a model, which can encode both the latent dependent structure due to the common topics and the remaining sparse ad-hoc dependent structure.
In Section \ref{sec:estimate}, we will discuss the assumptions in our model and penalization on likelihood function that is constructed in Section \ref{sec:model-form}.
In Section \ref{sec:theorem}, we provide a non-asymptotic error bound of the estimator.
Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem that is formulated in Section \ref{sec:estimate}.
In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.

@@

\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and an arbitrary matrix $L$, we assume that the eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad \mbox{where} \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T,
\]
where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$'s. If we have $L=F^TDF$, this condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.

@@

Directly maximizing the objective function in \eqref{eq:logistic08} is not going to be an easy task.
Following the approaches that were mentioned in Introduction, we propose to relax $F^T D F$ to $L$, where $L$ is a low rank matrix.
Consequently, the log-likelihood function in \eqref{eq:logistic08} can be rewritten as
\begin{eqnarray}
\label{eq:logistic09}
\mathbb{L}_n(\alpha,  L, S; X)
&=& \alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet L +\frac{1}{2} X \bullet S \\
&& -\sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + L_{ij} +S_{ij}}\right). \nonumber
\end{eqnarray}

@@

After we have obtained $\widehat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\widehat{S}$.
On the other hand when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
This is the price we have to pay for an amenable computational approach.
The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., the number of underlying common topics).
For the issue on assigning the community membership of each node $i$, we will discuss this later in Section \ref{sec:Num-anal}.

\section{Non-asymptotic error bound of the estimator}
\label{sec:theorem}
In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in a network is explicitly tracked. We are interested in solving the following optimization problem :
\begin{equation}\label{eq:Modified}
\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{\exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+\exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{equation}

@@

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L}) \label{Ass:2}
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
\end{assumption}

@@

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1}, \ref{Ass:2} and \ref{Ass:3},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2 \left\|\frac{1}{n}(X-P^{*}) \right\|_{op} \quad and \quad \gamma \geq 2\left\|\frac{1}{n}(X-P^{*})\right\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$
\begin{align} \label{theorem1}
    e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most $s$.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension of Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
whereas Agarwal, et al. \cite{agarwal2012noisy} work on a general linear observation model whose parameter is also
characterized by sum of a low rank matrix and a sparse matrix.

@@

\section{ Numerical analysis and Applications}
\label{sec:Num-anal}
Section \ref{sec:Num-anal} is divided into two parts.
In Section \ref{sec:Syn-dat}, we conduct an empirical study of our proposed method with artificial graphical structures.
In Section \ref{sec:citation_network}, we perform a real data analysis with citation network for statisticians.

@@

\subsubsection{Synthetic Setting} \label{sec:Syn-set}
%In this subsection, we consider the following $3$ scenarios:
%In this subsection, we consider $3$ scenarios.
%In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
%In second scenario, we study a more complicated situation than the first one where each paper in the network can possibly have more than one topic.
%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
%In third scenario, we consider a situation
Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
We put stars to the superscript of parameters to denote that they are ground truth.
Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and Section \ref{sec:model-form}.

@@

    \item Generate the weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$ $ \forall 1 \leq i \leq K$.
        In this way, we can let the papers with same topic cluster together.

    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
        This can be implemented via following steps:
        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
        \begin{align*}
           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\} \\
           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
           & \quad \vdots \\
           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\}
        \end{align*}
        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
        \[
            I_{S^*} =
            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
        \]
        where we use $i_r$ to indicate $r$th element $i$ in the set.
        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
        4) Lastly, make it symmetric by setting $S^*_{ji}=S^*_{ij},\forall 1\leq i < j \leq n$.
    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
\end{enumerate}

@@

\section{Appendix}
In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy}.
Then, we present Lemma \ref{le:le2} and its proof.
Finally, we present the proof of our Theorem\ref{Th:th1}.

>>>>

\documentclass[AMS,STIX1COL]{WileyNJD-v2}
%\documentclass[AMS]{WileyNJD-v2}
\usepackage{graphicx,times,verbatim,amsmath,amsthm}
%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{float}  % For fixing the image in draft
\usepackage{lscape}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\newcommand{\block}[1]{
  \underbrace{\begin{matrix}1 & \cdots & 1\end{matrix}}_{#1}
}

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{condition}[theorem]{Condition}
%\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{property}[theorem]{Property}
%\newtheorem{result}[theorem]{Result}
%\newtheorem{example}[theorem]{Example}
\newcommand{\Hquad}{\hspace{0.5em}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

@@

\keywords{citation network, matrix decomposition, latent variable model, logistic regression model, convex optimization, alternating direction method of multiplier}

\jnlcitation{\cname{%
\author{Suh Namjoon.},
\author{Xiaoming Huo},
\author{Eric Heim},
\author{Timothy Van Slyke}, and
\author{Lee Seversky}} (\cyear{2019}),
\ctitle{Citation network}, \cjournal{journal.}, \cvol{2019;00:1--6}.}
\maketitle
\footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, alternating direction method of multiplier, network model}

@@

\begin{equation}
\label{eq:logistic01}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha + f_i^T D f_j }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$.
We assume $d_{i} > 0$ for $1 \le i \le K$.
Another way to put \eqref{eq:logistic01} is
\begin{equation}
\label{eq:logistic02}
\mathbb{P}(X_{ij}=1) = \frac{\exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}{1 + \exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}.
\end{equation}
A justification of the above model is that when both node $i$ and node $j$ are related to topic $k$, they have a higher chance to cite one way or the other.
We have assumed a common strength coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes.
We denote a matrix $F = \{f_1, f_2, \ldots, f_n\} \in \mathbb{R}^{K \times n}$.
Each column $i$ in matrix $F$ contains the factor loadings associated with the node $i$ ($1\le i \le n$).
Given the diagonal matrix $D$ and the factor loading matrix $F$, we assume that $X_{ij}$'s are independent; therefore we have the total conditional probability function as follows:
\begin{equation}
\label{eq:logistic03}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \prod_{1\le i<j \le n} \mathbb{P}(X_{ij})
= \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha + f_i^T D f_j) }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\mathbb{P}(X_{ij})$ is given in \eqref{eq:logistic02}.
The last equation holds because $X_{ij}$ only takes binary (i.e., $0$ or $1$) values.
Recall that the dot product of two matrices with same dimensionality, $A,B\in \mathbb{R}^{a \times b}$, is defined as $A\bullet B=\mbox{trace}(A^T B) = \sum_{i=1}^a\sum_{j=1}^b a_{ij}b_{ij}$.
The above \eqref{eq:logistic03} can be further rewritten as
\begin{equation}
\label{eq:logistic04}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F)\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where we assume $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
The above delivers a factor analysis model.
Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g., \cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).

@@

Though it may seem similar to Chen et al \cite{chen2016fused}, we work on a different model formulation in several aspects.
We summarize the differences as follows.
\begin{enumerate}
\item FLaG is built to analyze the Eysenck's Personality Questionnaire that consists of items designed to measure Psychoticism, Extraversion, and Neuroticism.
    So there are $p$ questions that need to be answered, and each questions fall into above three categories.
    If there are $n$ respondents to questions, they have $n$ independent data generated from the same distribution.
    In our case, the observed citation network can be thought of as one realization of a random graph.

@@

\item FLaG approximates the original likelihood through constructing pseudo-likelihood function by taking advantage of conditional independence among the nodes.
    In our model, likelihood function is directly accessible due to the conditional independence among edges.
\end{enumerate}

@@

The rest of the paper is organized as follows.
In Section \ref{sec:model-form}, we will give a presentation on how to build a model, which can encode both the latent dependent structure due to the common topics and the remaining sparse ad-hoc dependent structure.
In Section \ref{sec:estimate}, we will discuss the assumptions in our model and the penalization on the likelihood function, which is constructed in Section \ref{sec:model-form}.
In Section \ref{sec:theorem}, we provide a non-asymptotic error bound of the estimator.
Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem.
In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on a real citation network of statisticians.
We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.

@@

\item Following the approaches that were mentioned in the Introduction, we propose to relax $F^T D F$ to $L$, where $L$ is a low rank matrix.
Furthermore, to ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and an arbitrary matrix $L$, we assume that the eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad \mbox{where} \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T,
\]
where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$'s. Since we have $L=F^TDF$, this condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.

@@

Directly maximizing the objective function in \eqref{eq:logistic08} is not going to be an easy task.
Consequently, the log-likelihood function in \eqref{eq:logistic08} can be rewritten as
\begin{eqnarray}
\label{eq:logistic09}
\mathbb{L}_n(\alpha,  L, S; X)
&=& \alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet L +\frac{1}{2} X \bullet S \\
&& -\sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + L_{ij} +S_{ij}}\right). \nonumber
\end{eqnarray}

@@

After we have obtained $\widehat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\widehat{S}$.
On the other hand, when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
This is the price we have to pay for an amenable computational approach.
The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., the number of underlying common topics).
We will discuss the issue on assigning the community membership of each node $i$ later in Section \ref{sec:Num-anal}.

\section{Non-asymptotic error bound of the estimator}
\label{sec:theorem}
In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in a network is explicitly tracked. We are interested in solving the following optimization problem :
\begin{equation}\label{eq:Modified}
\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{\exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+\exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1.
\end{equation}

@@

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L}) \label{Ass:2}
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes an all one vector in $\mathbb{R}^{n}$.
\end{assumption}

@@

\begin{theorem} \label{Th:th1}
Under the Assumptions \ref{Ass:1}, \ref{Ass:2} and \ref{Ass:3},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2 \left\|\frac{1}{n}(X-P^{*}) \right\|_{op} \quad and \quad \gamma \geq 2\left\|\frac{1}{n}(X-P^{*})\right\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$
\begin{align} \label{theorem1}
    e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most $s$.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension of Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
whereas Agarwal, et al. \cite{agarwal2012noisy} work on a general linear observation model whose parameter is also
characterized by a sum of a low rank matrix and a sparse matrix.

@@

\section{ Numerical analysis and Applications}
\label{sec:Num-anal}
Section \ref{sec:Num-anal} is divided into two parts.
In Section \ref{sec:Syn-dat}, we conduct an empirical study of our proposed method with synthetic graphical structures.
In Section \ref{sec:citation_network}, we perform a real data analysis with a citation network for statisticians.

@@

\subsubsection{Synthetic Setting} \label{sec:Syn-set}
%In this subsection, we consider the following $3$ scenarios:
%In this subsection, we consider $3$ scenarios.
%In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
%In second scenario, we study a more complicated situation than the first one where each paper in the network can possibly have more than one topic.
%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
%In third scenario, we consider a situation
Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.
We put astroids in the superscript of parameters to denote that they are ground truth.
Readers can refer the meaning of each parameter in the model in Section \ref{sec:intro} and Section \ref{sec:model-form}.

@@

    \item Generate the weight coefficients of the factors $D^*_{ii}$ from the uniform distribution that is supported on $[19,20]$, $ \forall 1 \leq i \leq K$.
        In this way, we can leave the papers with same topic cluster together.

    \item Recall that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
        Specifically, we assume that there are $\frac{|S^*|}{\binom{K}{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
        This can be implemented via following steps:
        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
        \begin{align*}
           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\} \\
           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
           & \quad \vdots \\
           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\}
        \end{align*}
        where each of them has arbitrary $\frac{|S^*|}{\binom{K}{2}}$ elements.
        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
        \[
            I_{S^*} =
            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{\binom{K}{2}} \bigg\},
        \]
        where we use $i_r$ to indicate $r$th element $i$ in the set.
        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
        4) Lastly, make it symmetric by setting $S^*_{ji}=S^*_{ij},\forall 1\leq i < j \leq n$.
    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
\end{enumerate}

@@

\section{Appendix}
In this Section, first we briefly introduce several notations, a notion on the decomposability of regularizer, and a useful lemma proved in the work \cite{agarwal2012noisy} (Section\ref{App:Pre}).
Then, we present Lemma \ref{le:le2} and its proof (Section \ref{App:Lemma2}).
Finally, we present the proof of our Theorem\ref{Th:th1} (Section \ref{App:Theorem1}).
